\subsubsection{Application Survey}
The current main developer of new features is Johannes Wolf. 
He is supported by Johannes Linke who is mainly responsible for a good coding style, including code review and refactoring. 
We interview them about information regarding the first steps of our project.

\paragraph{Development Paradigm and Development Languages}
There are no development paradigms explicitly determined.
But as stated there is a main developer responsible for code review.
As it is all newly developed code is reviewed before it is accepted.
Everyone is able to review code and discuss it with the coder and other reviewers.
This practice shall ensure readable code and distribute knowledge about code changes.
Additionally, it is implicitely assumed that paradigms of the used development languages are followed.
The development languages are:
\begin{itemize}
    \item Python 3 through the Django framework
    \item HTML
    \item Javascript
    \item CSS
\end{itemize}
As an example for paradigms given by the languages we checked the document known as \emph{PEP 0008}.
This is the style guide for Python code written by Guido van Rossum, the author of Python, and followed by most open source projects in Python.
Link: \url{https://www.python.org/dev/peps/pep-0008/}

\paragraph{Requirements / Specification / Documentation / Artefacts}
Github Wiki
(Janno)

\paragraph{Current testing status / Bug repositories}

GitHub, TravisCI, gemnasium, landscape

\paragraph{Personal involvement}

User, tester, developer
