\subsubsection{Initial Test Plan}
We developed an initial plan based on our findings in the application survey.
As suggested we followed the questions discussed during the lecture.
The test plan includes evaluating and enhancing the existing artifacts, cross-checking the results found by the tools used and eventually improving the testing status.

\paragraph{Five V\&V Questions}
We started with evaluating EvaP regarding the five basic verification and validation questions:
\begin{enumerate}
	\item When do verification and validation start? When are they complete?
    
    Verification and validation started along the start of the project and will be an important part during the duration of the project. 
	\item What particular techniques should be applied during development?
    
    As EvaP is a software too big to be wholly tested by us within the scope of the seminar project, we will try to apply as many techniques as possible on a small subpart of the project. We will evaluate the techniques and make recommendations for further testing to the main developers.
	\item How can we assess the readiness of a product?
    
    Since EvaP is already in use it is certainly ready. Our testing will not influence the readiness.
	\item How can we control the quality of successive releases?
    
    Additionally to continous integrationa and automated tests, a code review before merge is already implemented in the development process to control the quality of successive releases. We hope to enable developers to gain more knowledge about the system by enhancing the available artifacts and documentation.
	\item How can the development process itself be improved?
    
    The main weakness of the development process is the sparse distribution of knowledgeand the change of developers over time. Since only students are interested in developing EvaP we do not see a possibility to improve this part of the process.
\end{enumerate}

\paragraph{Test Classifications and Approaches}
\begin{enumerate}
    \item Validation vs. Defect Testing
    
    \item Development, Release, User Testing 
    
    \item Unit/Component, Integration, System Testing
\end{enumerate}


\paragraph{Coverage-based Testing}

\paragraph{Initial Test Plan}
